How to use replication assignments for teaching integrity in empirical archaeology

### 2019-08-15 analysis/paper/paper.Rmd
send the ms. to co-authors for final approval after peer reviews
mention that we have examples of student submissions on OSF

To enable re-use of our materials and improve reproducibility and transparency according to the principles outlined in @marwick2017open, we include all our assignment materials, as well as the entire R code used for all the analysis and visualizations contained in this paper, in our compendium at http://doi.org/10.17605/OSF.IO/DBSW9. Also in this version-controlled compendium are the raw data for the analyses reported here. The figures and results presented here can be independently reproduced with the code and data in this repository. In our compendium our code is released under the MIT license, our data as CC-0, and our figures and assignment materials as CC-BY, to enable maximum re-use [for more details, see @Marwick2017].

@@

The final task was for the students to write their report, and submit a reproducible research compendium. This included three files: (1) their R Markdown document, (2)  the raw data file, and (3) the output document (e.g. Microsoft Word document that is produced when they knit the R Markdown file). The students submitted these materials to Canvas for grading. We did not make the student work public, unlike some of examples described above that deposit student work in public on the Open Science Framework. Our expectation was that we could reproduce any student’s results by running their submitted R Markdown document with the raw data file to produce the Word document they submitted. The final report was graded with a rubric which was presented to the students at the first step to help set expectations about what the final product should look like.

@@

Thanks to the students of ARCHY 483 in Spring 2019 for participating in the assignment.

>>>>

To enable re-use of our materials and improve reproducibility and transparency according to the principles outlined in @marwick2017open, we include all our assignment materials, as well as the entire R code used for all the analysis and visualizations contained in this paper, in our compendium at http://doi.org/10.17605/OSF.IO/DBSW9. Also in this version-controlled compendium are the raw data for the analyses reported here. The figures and results presented here can be independently reproduced with the code and data in this repository. In our compendium our code is released under the MIT license, our data as CC-0, and our figures, and assignment instructions and grading rubric as CC-BY, to enable maximum re-use [for more details, see @Marwick2017].

@@

The final task was for the students to write their report, and submit a reproducible research compendium. This included three files: (1) their R Markdown document, (2)  the raw data file, and (3) the output document (e.g. Microsoft Word document that is produced when they knit the R Markdown file). The students submitted these materials to Canvas for grading. Two complete student submissions are available for inspection in our compendium at http://doi.org/10.17605/OSF.IO/DBSW9. We did not make all the student work public, unlike some of examples described above that deposit student work in public on the Open Science Framework. Our expectation was that we could reproduce any student’s results by running their submitted R Markdown document with the raw data file to produce the Word document they submitted. The final report was graded with a rubric which was presented to the students at the first step to help set expectations about what the final product should look like.

@@

Thanks to the students of ARCHY 483 in Spring 2019 for participating in the assignment. Thanks to the peer reviewers for their detailed feedback and suggestions for improvement.
